Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-31 chapters/introduction/introduction.tex
minor changes

So far, we have explained four important related computer vision
concepts. In the following section, we are going to discuss our main
contributions.

@@

We make contributions in three main areas: 1) we proposed a general
probabilistic model to jointly estimate the geo-calibration
parameters, 2) we decomposed the full geo-calibration into several
partial geo-calibration tasks, each of which provides a strong
constraint function that fits into the general model, and 3) we show
that learning to geo-calibrate a camera is a useful pretext for image
feature learning.

The first two contributions make our main approach. Our
algorithm feeds inputs (images, time and manual annotations) to
different constraint functions. Then
we fuse these constraint functions to simulate the joint distribution
over the complete geo-calibration parameters. We present the flowchart of
our approach in \figref{intro:architecture}.
%
Furthermore, we also explore to learning image features
and geo-calibrating cameras simultaneously.  We believe that camera
poses, geographic locations and image capture times are closely
related to image representations. 
Based on the belief that visual features which abstract the image
contents are the necessary for solving the geo-calibration tasks, we
designed neural networks to learn useful visual features by
geo-calibrating cameras. Our work provide new ways for automatic
feature learning.

\subsection{General Probabilistic Model for Geo-Calibration}
We design a general model to estimate the probability over all
geo-calibration parameters. First, we model the process of projecting
from the scene at given location, time, and in given camera pose.
%This the appearance of the image frame are determined by the pin-hole
%model and the geographic location of the camera.
We use a scoring function to measure the ``fitness'' between these
geo-calibration parameters and the appearance of the image. 
The scoring function is proportional to the probability distribution
over the geo-calibration parameters, but the denominator is unknown. We
then propose a Markov Chain Monte Carlo (MCMC) sampling approach to
approximate the underlying probability distribution.
Our model is flexible that it is able to contribute different
constraint functions to the scoring function. The details of this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In the general model, we define the scoring function as a weighted
summation of a series of constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different sets of geo-calibration parameters. 
A constraint function outputs a score or probability for some given
geo-calibration parameters conditional on the input image.

>>>>

We have explained four related computer vision concepts so far. In the
following section, we are going to discuss our main contributions.

@@

In this thesis, we make contributions in three main areas: 1) we
proposed a reflexible probabilistic model to jointly estimate the
geo-calibration parameters, 2) we decomposed the full geo-calibration
into several partial geo-calibration tasks, each of which provides a
strong constraint function that fits into the probabilistic model,
and 3) we show that learning to geo-calibrate a camera is a useful
pretext for image feature learning.

The first two contributions make our main approach. Our
algorithm feeds inputs (images, time, and manual annotations) to
different constraint functions, which we can fuse together to simulate
the joint distribution over the complete geo-calibration parameters.
We present the flowchart of our approach in
\figref{intro:architecture}.
%
Furthermore, based on the belief that the content of the image is usually dictated
by the camera pose, geographic location and image capture time. We
treat geo-calibration information as pretext task and show that they
are useful for image feature learning.

\subsection{Flexible Probabilistic Model for Geo-Calibration}
We design a flexible probabilistic model to estimate the probability
over all geo-calibration parameters.
First, we construct a scoring function to model the process of camera
projecting the scene to image frame at given pose, location, and time.
%
The scoring function consists of a series of constraint functions,
which measures the ``fitness'' between these geo-calibration
parameters and the appearance of the image. 
%
The scoring function is proportional to the probability distribution
over the geo-calibration parameters. Since the integral over all
possible parameters is intractable, We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution. 
%
Our model is flexible that it allows different constraint functions
contribute to the scoring function. The details of this model can be
found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
The scoring function of the probabilistic
model is defined as a weighted summation of a series of constraint
functions.
A constraint function outputs a score (or probability) of the input
geo-calibration parameters given the input image. In the rest of the
work, we focus on developing good constraint functions for different
sets of geo-calibration parameters.
